\documentclass[10pt]{article} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Common preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PAGE
%% \usepackage{fullpage}
% FONTS
\usepackage{url} % enhanced version of computer modern
\urlstyle{same}
%%\usepackage{lmodern} % enhanced version of computer modern
\usepackage[T1]{fontenc} % for hyphenated characters
%%\usepackage{amssymb}
%%\usepackage{mathtools} % contains amsmath which comes with align
%%\usepackage{amsthm}
%%\usepackage{microtype} % some compression
%%
%% REFERENCING DOES NOT WORK WITH BIBENTRY PACKAGE
\usepackage{natbib}
\usepackage[colorlinks=true,pdfborder={0 0
0},citecolor=magenta,linkcolor=magenta]{hyperref}

\usepackage{bibentry}
% LISTS
%%\usepackage{enumerate}
% ROMAN NUMERALS
\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble ends
%% from now on, draft specific
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\textwidth}{5.1in} % Text width of the document
%%\usepackage{etoolbox}
%%\usepackage{multicol}
%% adding footer
%%\usepackage{fancyhdr}
%%\usepackage{xcolor}
%%\fancypagestyle{mypagestyle}{%
%%\fancyhf{}%
%%\fancyfoot[C]{\textcolor{red}{\thepage}}%
%%}
\rfoot{\textcolor{gray}{Updated on \today}}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\pagenumbering{gobble}
%% \newtoggle{visa}
%% \newtoggle{compact}
%% \toggletrue{visa} % comment this if you want normal resume
%% \toggletrue{compact} % comment this if you want normal resume
%% 
\begin{document}
\thispagestyle{fancy}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
%%  
%% \section{OBJECTIVE}  
%% 
%% A position in the field of computers with special interests in business applications programming, information processing, and management systems. 
%% 
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{\textnormal{\textsc{Contact Information}}}
Network Systems Science and Advanced Computing (NSSAC)\\
Biocomplexity Institute and Initiative\hfill \texttt{email:}
abhijin@virginia.edu\hspace{0mm}\mbox{}\\
University of Virginia\hfill \texttt{phone:}
\texttt{+}1 540 204 6679\hspace{6.5mm}\mbox{}\\
Biocomplexity Institute \\
995 Research Park Blvd. 4th Floor \\
Charlottesville, VA 22911 \\
\url{http://people.virginia.edu/~aa5ts}
%%
\section{\textnormal{\textsc{Current\,\,\,\, Position}}}
\textbf{Research Assistant Professor} \hfill Oct 2018 -- present\\
Network Systems Science and Advanced Computing (NSSAC)\\
University of Virginia
%%%%
\section{\textnormal{\textsc{Research Interests}}}
Network science, algorithm theory, combinatorics,
Computational modeling, 
Game theory and Machine learning\\
{\bf Applications:} Invasive species spread, computational
epidemiology, modeling and analysis of large socio-technical systems
%%%%
\section{\textnormal{\textsc{Education}}}
\textbf{PhD:} \hfill August 2006 -- March 2011\\
Dept. of Computer Science and Automation\\
Indian Institute of Science, Bangalore, India\\ 
%% Adviser: {Dr. L Sunil Chandran}\\
%% {Thesis}: On Dimensional Parameters of Graphs and Posets\\
~\\
\noindent\textbf{Master of Science (Engg):} \hfill August 2001 -- August 2003\\
Dept. of Electrical Engineering,\\
Indian Institute of Science, Bangalore, India\\
%% Adviser: Dr. K R Ramakrishnan\\
%% {Thesis:} Cyclic Multirate Structures Based on Symmetric-Periodic
%% Sequences\\
~\\
\noindent\textbf{Bachelor of Engineering:} \hfill 1996 -- 2000\\
Bangalore University (B.M.S. College of Engineering)\\
Telecommunication Engineering
%%%%%%
\section{\textnormal{\textsc{Work\,\,\,\, Experience}}} 
{Research Assistant Professor} \hfill Jul 2016 -- Oct 2018\\
Senior Research Associate \hfill May 2014 -- Jul 2016\\
Postdoctoral Associate \hfill October 2011 -- May 2014\\
Network Dynamics and Simulation Science Laboratory\\
Biocomplexity Institute of Virginia Tech\\
~~~\\
Research Associate \hfill March 2011 -- September 2011\\
Dept. of Computer Science and Automation, IISc \\
~~~\\
{Beceem Communications Pvt Ltd}\hfill August 2004 -- July 2006\\
Algorithm design for WiMax (802.16) \\
~~~\\
Project Associate \hfill October 2003 -- April 2004\\ 
Project Associate\hfill October 2000 -- August 2001\\ 
Dept. of Electrical Engineering, IISc \\
%% Worked under Dr. P S Sastry on temporal data-mining \\
%% Worked under Dr. K R Ramakrishnan on source \& channel coding and Advanced
%% Encryption Standard (Rijndael)
%%%%%%
\clearpage
\section{\textnormal{\textsc{Grants}}}
\begin{enumerate}[$\circ$]
\item USDA NIFA Foundational and Applied Science Program: \emph{Network
Models of Food Systems and their Application to Invasive Species Spread} \\
Amount:~\$400,000; Duration: Sep'19--Aug'23\\
Role: PI
\item USAID Egypt Mission: \emph{Pest Risk Assessment of the Fall Armyworm,
Spodoptera frugiperda in Egypt}\\ Amount:~\$18,000; Duration:
Oct'17--Dec'17\\ Role: Co PI
%\item
%\noindent\textbf{Pending}\\
\item USAID IPM Innovation Labs: \emph{A High-resolution Interaction Based
Approach to Modeling the Spread of Agricultural Invasive Species}\\
Amount:~\$1,000,000 (\$800,000 for Virginia Tech); Duration: Oct'15--Nov'20\\
Role: PI
\end{enumerate}
%%%%%%%%%%%%
\section{\textnormal{\textsc{Awards}}}
\begin{enumerate}[$\circ$]
   \item ``DSFEW Early Career Researchers Travel Fund'', KDD 2016.
\item ``Honorable Mention For Outstanding Novelty of Research
Question'' award for the paper ``Sensitivity of Diffusion Dynamics to
Network Uncertainty'' in AAAI'13.
\item Infosys Fellow: awarded to select
PhD candidates in IISc by Infosys Technologies Ltd. 
\item Secured All India Rank of 34 in GATE 2000 (EC), a national level
entrance exam for post graduate studies.
\item Ranked 7th in Bangalore University in Telecommunication Engg. (Year 2000).
\end{enumerate}
%%
\section{\textnormal{Memberships}}
\begin{enumerate}[$\circ$]
\item IEEE member
\end{enumerate}
%%
%%
\section{\textnormal{\textsc{News}}}
\begin{enumerate}[$\circ$]
\item
\href{https://vtnews.vt.edu/articles/2018/03/outreach-ipmegyptfaw.html}{Virginia Tech provides key intel in U.S. and Egyptian-led battle against a major pest}
\item
\href{https://vtnews.vt.edu/articles/2018/02/outreach-ipmnexus.html}{Countries
get heads up about leafminer invasion thanks to Virginia Tech} (also picked
up by Wisconsin Farmer and Agrilinks)
\item
\href{https://vtnews.vt.edu/articles/2016/05/outreach-oiredinnovationlabawards.html}{Virginia Tech awards more than \$11 million to help feed people in
developing countries}
\item
\href{https://www.bi.vt.edu/ndssl/news/virginia-tech-research-team-fights-the-spread-of-invasive-pests}{Virginia
Tech Research Team Fights the Spread of Invasive Pests}
\end{enumerate}
%%
\section{\textnormal{\textsc{Selected Talks}}} 
\begin{enumerate}[1.]
    \item Understanding the Role of Seasonal Food Trade Networks in Invasive
Species Spread, SIAM Network Science, Snowbird, Utah,
    May 2019.
    \item How to stop an epidemic? Networked dynamical systems, games and
    near-optimal algorithms, Indian Institute of Technology, Dharwad,
    October 2018.
    \item Multi-pathway models to assess the threat of invasive species
    spread, Indian Agricultural Research Institute, Delhi, October 2018
    (invited).
    \item Multi-pathway models to understand the spread and impact of Tuta
    absoluta, International Conference on Biological Control (ICBC),
    September 2018.
   \item Webinar: New Approaches to Control the South American Tomato
   Leaf Miner \emph{Tuta absoluta}, April 2018
   \item Monitoring the spread of {\it Tuta absoluta} using a
    multi-layered network based modeling framework, \emph{9th International
    IPM Symposium}, Baltimore, March 2018
    \item Modeling the Spread of Fall Armyworm, \emph{Fall Armyworm
    Workshop}, Adis Ababa, 2017
    \item Understanding the role of human-mediated pathways in pest spread:
    Case study of \emph{Tuta absoluta}, \emph{12th Arab Congress of Plant
    Protection}, Hurghada, 2017
   \item Monitoring spread of T. absoluta using a multi-layered network
   based modeling framework, \emph{Symposium on Global Spread and Management
   of the South American Tomato Leafminer, Tuta absoluta. International
Congress of Entomology}, Orlando, 2016
\item How to stop an epidemic?  Games and near-optimal algorithms,
\emph{Dept. of Computer Science and Automation, Indian Institute of
Science}, Bangalore, 2014
\item Sensitivity of Dynamical Properties to Network Uncertainty,
\emph{Dept. of Computer Science and Automation, Indian Institute of
Science}, Bangalore, 2013
\end{enumerate}
%%
\iftoggle{compact}{
\section{\textnormal{\textsc{Selected publications}}} 
}{
\section{\textnormal{\textsc{Publications}}} 
}
\nobibliography*
\noindent\textbf{Journal articles}\\
\begin{enumerate}[1.]%%[$\circ$]
\item \bibentry{mcnitt2019assessing}
\item \bibentry{maharjan2019predicting}
\item \bibentry{venkatramanan2019modeling}
\iftoggle{compact}{}{
\item \bibentry{adiga2018graphical}
}
\item \bibentry{adiga2018disparities}
\iftoggle{compact}{}{
\item \bibentry{adiga2018sublinear}
}
\item \bibentry{camposwestern}
\iftoggle{compact}{}{
\item \bibentry{adiga2017inferring}
\item \bibentry{adiga2017activity}
}
\item \bibentry{zhang2016near}
\item \bibentry{adiga2014sensitivity}
\item \bibentry{adiga2014representing}
\iftoggle{compact}{}{
\item \bibentry{adiga2014constant}
\item \bibentry{wu2014limit}
}
\item \bibentry{adiga2014lower}
\iftoggle{compact}{}{
\item \bibentry{adiga2014cubicity}
}
\item \bibentry{adiga2011boxicity}
\item \bibentry{adiga2010hardness}
\item \bibentry{adiga2010cubicity}
\item \bibentry{adiga2009cubicityThreshold}
\end{enumerate}
\noindent\textbf{Refereed conference proceedings}\\
\begin{enumerate}[1.]%%[$\circ$]
\item \bibentry{adiga2019validating}
\item \bibentry{hu2019modeling}
\item \bibentry{adiga2019pac}
\iftoggle{compact}{}{
\item \bibentry{cedeno2019mechanistic}
\item \bibentry{ren2018generative}
}
\item \bibentry{adiga2018learning}
\iftoggle{compact}{}{
\item \bibentry{adiga2017kserver}
\item \bibentry{venkat2017towards}
}
\item \bibentry{adiga2016delay}
\item \bibentry{adiga2016temporal}
\iftoggle{compact}{}{
\item \bibentry{adiga2015csd}
}
\item \bibentry{zhang2015group}
\iftoggle{compact}{}{
\item \bibentry{adiga2015inferring}
\item \bibentry{adiga2015network}
\item \bibentry{adiga2015effect}
}
\item \bibentry{saha2015spectrum}
\item \bibentry{saha2014game}
\iftoggle{compact}{}{
\item \bibentry{adiga2013modelingurban}
}
\item \bibentry{adiga2013subgraph}
\item \bibentry{adiga2013robust}
\item \bibentry{adiga2013sensitivity}
\item \bibentry{adiga2012representing}
\iftoggle{compact}{}{
\item \bibentry{adiga2012polynomial}
\item \bibentry{adiga2011cubicity}
\item \bibentry{adiga2011constant}
\item \bibentry{adiga2010parameterized}
\item \bibentry{adiga2010boxicity}
\item \bibentry{adiga2009cubicity}
\item \bibentry{adiga2003design}
}
\end{enumerate}
\iftoggle{compact}{}{
\noindent\textbf{Workshop/poster}\\
\begin{enumerate}[1.]
\item \bibentry{adiga2019inferring}
\item \bibentry{adiga2019understanding}
\item \bibentry{nath2018using}
\item \bibentry{adiga2018using}
\item \bibentry{adiga2018inferring}
\item \bibentry{geneiusWu}
\item \bibentry{hybridModelsVenkat}
\item \bibentry{climexSridhar}
\item \bibentry{venkat2016kdd}
\item \bibentry{adiga2015bme}
\item \bibentry{adiga2015synthetic}
\item \bibentry{adiga2012route}
\end{enumerate}
\noindent\textbf{Reports}\\
\begin{enumerate}[1.]
\item \bibentry{heinrichs2018pest}
\end{enumerate}
}
%% \noindent\textbf{Under review/Technical reports}\\
%% \begin{enumerate}[1.]
%% \item \bibentry{mortveit2015synthetic}
%% \item \bibentry{adiga2015sublinear}
%% \item \bibentry{adiga2015interaction}
%% \end{enumerate}
%%
\section{\textnormal{\textsc{Students \\Current/Past}}}
\noindent\textbf{PhD}\\
Sichao Wu (Thesis adviser: Henning Mortveit)\vspace{.2cm}\\
\noindent\textbf{Masters}\\
Daniel Perez Lazarte (project)\\
Joseph McNitt (Thesis adviser: Henning Mortveit)\vspace{.2cm}\\
\noindent\textbf{Undergraduates}\\
Surbhi Singh (Fall'19),
Ethan Choo (Summer'19),
Katie Liu (Summer'19),
Bryan Kaperick (Spring'16--Spring'17), and
Amleshwar Kumar (Intern: Fall'16)
\section{\textnormal{PhD \textsc{Committees}}}
Sudip Saha (NDSSL, VBI, Virginia Tech)
%%
\section{\textnormal{\textsc{Professional Service}}}
\noindent\textbf{Technical Program Committee member}\\ 
AIKE~(2019, 2018), INFOCOM~(2019), CSoNet~(2016), CONECCT~(2015), SDM-Networks~(2015), SIAMNS~(2015)\smallskip\\
\noindent\textbf{Grant Review}\\
NSF~(2018) (Grant review panelist)\\
National Fund for Scientific and Technological Development (FONDECYT),
Chile\smallskip\\
\noindent\textbf{Reviewer}\\ 
\noindent
Applied Network Science (2019),
International Journal of epidemiology~(2019),
Pest Management Science~(2019), 
Journal of Parallel and Distributed Computing~(2019), 
Journal of Pest Science~(2018), 
Australasian Journal of Combinatorics~(2018, 2015),
FPSAC~(2017),
ACM Transactions on Algorithms~(2017),
Journal of Royal Society Interface~(2017), INFOCOM~(2016, 2015), Order~(2015), 
Algorithmica~(2014), Journal of Autonomous Agents and Multi-Agent
Systems~(2013), 
Information Processing Letters~(2012), 
Graphs and
Combinatorics~(2011), CATS~(2011)\bigskip\\
\iftoggle{compact}{}{
\noindent\textbf{Miscellaneous}\\ 
\begin{enumerate}[$\circ$]
\item Student and postdoc hiring committee in NSSAC 2018-present
\item Student and postdoc hiring committee in NDSSL 2017-2018
\item Member of graduate students admission team in NDSSL for the Fall'16
admissions
\item Organized NDSSL graduate seminar series for the academic year 2013-2014
\end{enumerate}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For visa
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iftoggle{visa}{
\newpage
\section{\large{Job description}:}
\vspace{.8cm}
%%
\section{\textnormal{{Current job}}}\label{sec:currentJob}
My work is in the areas of network science, algorithms, combinatorics and
game theory. My research focus is on the design and analysis of
computational models and their application to solve real-world problems.
Through interdisciplinary collaborative efforts, I (i)~contribute to the
understanding of structural and dynamical properties of networks,
(ii)~develop efficient and practical algorithms for various optimization
problems, and (iii)~take part in the design and implementation of complex
simulation systems. Some of the application areas of my work include
invasive pest modeling, computational epidemiology, transportation and
social sciences.
%%
\section{\textnormal{{Senior Research Associate}}}\label{sec:sra}
(May 2014 -- Jul 2016) Job description is same as current
job.\smallskip
%%
\section{\textnormal{{Postdoctoral associate}}}\label{sec:postdoc}
(October 2011 -- May 2014) Job description is same as current
job.\smallskip
%%
\section{\textnormal{{Research associate}}}
(March 2011 to October 2011) I continued my PhD work.\smallskip
%%
\section{\textnormal{PhD}}
(August 2006 to March 2011)
The work of this thesis falls into the broad area of theoretical computer
science, and in particular, concerns graph theory, combinatorics and
algorithms. We study some geometric representations of graphs and
dimensional properties of graphs and posets. The main objective is
to represent a graph using certain geometric objects. Many problems
on graphs which are otherwise computationally hard to solve can be
solved efficiently if the graph in consideration has a simple geometric
representation. In the parlance of theoretical computer science, many
NP-hard problems may be either solved in polynomial time or at least
have good approximation algorithms when a graph has a low dimensional
geometric representation. Besides, the representations which we consider
have applications in various other scientific disciplines: ecology,
social sciences, psychology, telecommunication and operations research.
Our contribution to this area are as follows:
(1)~We have developed efficient algorithms to
obtain such representations for certain specific classes of graphs.
(2)~We have complexity results which show that for some classes of graphs, it
is computationally hard to obtain such a representation.
(3)~We give a general framework relating different representations.
%%
\section{\textnormal{Beceem Communications}}\label{sec:beceem}
(August 2004 -- July 2006)
I was part of the algorithm development and simulation group. My
work involved the design and implementation of algorithms for WiMax
(802.16), a wireless broadband standard. I worked on (1)~implementing
and maintaining the error control coding module in the simulator, 
%I had
%to implement the turbo encoder and decoder, a class of high-performance
%forward error correction (FEC) codes. The language in which the simulator
%was implemented was MATLAB.
(2)~The creation of an interface between
the simulator (coded in MATLAB) and the chip (coded using Verilog), 
%I was involved in this project right from its initiation. This interface
%provided the vital link between the two modules and enabled the
%verification.
(3)~Running simulations by
varying parameters such as type of codec, channel, etc.
%%
\section{\textnormal{Project associate}}\label{sec:dataMining}
(October 2003 to April 2004)
The work was in the area of temporal data-mining. 
%We were given access
%to months of data from a manufacturing line of a factory. Each time
%the manufacturing process stopped, the time and the reason behind
%the stoppage was logged into the system. The reasons could be anything
%ranging from the mundane (like a lunch break!) to the very technical ones.
%Each possible reason for stoppage was represented by a symbol. Hence,
%the data given to us was in the form of very long sequences of symbols
%with time stamp. 
The aim was to extract interesting patterns from a sequence of logs
obtained from a manufacturing process by using machine learning techniques.
%The main question
%that our tool had to answer was: Does a particular sequence of breakdowns
%in one section of the manufacturing line influence a breakdown in some
%other section?
%My work was mainly implementation oriented and could be divided into two
%parts.  Firstly, 
I helped in the development of the data mining tools for this purpose.
%to filter the data 
%(like
%for example, removing the symbols corresponding to lunch break). This
%required using some scripting languages. Secondly, 
%I had to assist in
%enhancing our data mining tool by implementing new search techniques. The
%language of implementation was C.
%
%I was also involved in administrative activities related to the project and
%conducting exams.
%%
\section{\textnormal{MSc}}\label{sec:mastersAbstract}
(August 2001 to September 2003)
%This work is in the area of digital signal processing. 
We proposed a
framework for implementing wavelet transforms in the frequency domain
particularly for application on images and analyzed the performance of our
methods in the context of image compression by comparing our methods with
the methods used in JPEG and JPEG 2000 image compression
standards. 
%%
\section{\textnormal{Project associate}}\label{sec:turbo}
(October 2000 -- August 2001)
I worked in the area of communication theory. My work involved studying
the area of joint source and channel coding and other areas related to
telecommunication. I implemented some algorithms like turbo codecs and
Rijndael in MATLAB and helped in administrative activities.

\newpage
\section{Personnel Manager Information}
\noindent{\bf Madhav V. Marathe}

\noindent Director, Network Dynamics and Simulation Science Laboratory
and Professor, Computer Science\\
\\
\noindent{\bf Mailing Address:} \\
\noindent Network Dynamics and Simulation Science Laboratory \\
\noindent Virginia Bioinformatics Institute \\
\noindent Virginia Polytechnic Institute and State University \\
\noindent Research Building XV (0477) \\
\noindent 1880 Pratt Drive \\
\noindent Blacksburg, VA 24061 \\
\noindent USA \\
\\
{\bf Tel:} 540-231-8252\\
{\bf Fax:} 540-231-2891\\
{\bf Email:} marathe@vt.edu\\
{\bf Web page:}
http://www.vbi.vt.edu/ndssl/people/people-profile/Madhav-Marathe \\
\\
\\
\noindent{\bf L. Sunil Chandran}\\
Associate Professor,
Department of Computer Science and Automation
Indian Institute of Science\\
\\
\noindent{\bf Mailing Address:} \\
CSA Department\\
Indian Institute of Science\\
Bangalore - 560012\\
\\
{\bf Tel:} +91-80-22932368\\
{\bf Fax:} +91-80-23602911 \\
{\bf Email:} sunil@csa.iisc.ernet.in\\
{\bf Web page:} http://drona.csa.iisc.ernet.in/\textasciitilde sunil/


   }{}
\end{resume}
\bibliographystyle{plain}
\nobibliography{mypapers}
\end{document}
