\documentclass[margin,10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Common preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PAGE
%% \usepackage{fullpage}
% FONTS
\usepackage{url} % enhanced version of computer modern
\urlstyle{same}
\usepackage{lmodern} % enhanced version of computer modern
\usepackage[T1]{fontenc} % for hyphenated characters
\usepackage{amssymb}
\usepackage{mathtools} % contains amsmath which comes with align
\usepackage{amsthm}
\usepackage{microtype} % some compression
%%
%% REFERENCING DOES NOT WORK WITH BIBENTRY PACKAGE
\usepackage{natbib}
\usepackage[colorlinks=true,pdfborder={0 0
0},citecolor=magenta,linkcolor=magenta]{hyperref}
\newcommand{\tuta}{\emph{T.~absoluta}}
\newcommand{\tutafull}{\emph{Tuta~absoluta}}

\usepackage{bibentry}
% LISTS
\usepackage{enumerate}
% ROMAN NUMERALS
\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble ends
%% from now on, draft specific
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\textwidth}{5.1in} % Text width of the document
\usepackage{etoolbox}
\usepackage{multicol}
%% adding footer
\usepackage{fancyhdr}
\usepackage{xcolor}
%%\fancypagestyle{mypagestyle}{%
%%\fancyhf{}%
%%\fancyfoot[C]{\textcolor{red}{\thepage}}%
%%}
\rfoot{\textcolor{gray}{Updated on \today}}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\pagenumbering{gobble}
\newtoggle{visa}
\newtoggle{compact}
%% \toggletrue{visa} % comment this if you want normal resume
%% \toggletrue{compact} % comment this if you want normal resume

\begin{document}
\thispagestyle{fancy}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

%\moveleft.5\hoffset\centerline{\large\bf Abhijin Adiga\hfill} % Your name at the top
\moveleft1.0\hoffset\centerline{\large\bf Abhijin Adiga\hfill} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
%%  
%% \section{OBJECTIVE}  
%% 
%% A position in the field of computers with special interests in business applications programming, information processing, and management systems. 
%% 
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{\textnormal{\textsc{Contact Information}}}
Network Systems Science and Advanced Computing (NSSAC)\\
Biocomplexity Institute and Initiative\hfill \texttt{email:}
abhijin@virginia.edu\hspace{0mm}\mbox{}\\
University of Virginia\hfill \texttt{phone:}
\texttt{+}1 540 204 6679\hspace{6.5mm}\mbox{}\\
\url{https://abhijin.github.io}
%%
\section{\textnormal{\textsc{Current\,\,\,\, Position}}}
\textbf{Research Assistant Professor} \hfill 2016 -- present\\
Network Systems Science and Advanced Computing (NSSAC)\\
University of Virginia
%%%%
\section{\textnormal{\textsc{Research interests and Focus}}}
Broadly, my interests are in network science, algorithm design,
combinatorics, machine learning and game theory. My current focus is on studying diffusion
processes using network dynamical systems and machine learning with
application to the spread of invasive species, infectious diseases, and
other socio-technical phenomena. There are three main thrusts to my
research.  Through large collaborative efforts, I design and analyze data- and
process-driven models using domain-specific knowledge. Secondly, I strive
to advance the theoretical foundations of such models to create robust
models that can be applied in data-poor environments. Thirdly, I develop
efficient practical solutions with provable guarantees for various
computational problems that arise in the target applications.\\

\section{\textnormal{\textsc{Publications summary}}}
Journals: 23\\
Conference proceedings: 33\\
Workshops/posters/abstract: 14\\

\section{\textnormal{\textsc{Grants summary}}}
PI: USAID \$1,100,000; USDA \$400,000\\
Co-PI: Two USAID grants \$170,000

\section{\textnormal{\textsc{Impact}}}
\begin{enumerate}[$\circ$]
\item USAID and USDA invasive species projects featured in Agrilinks,
Wisconsin Farmer, Charlottesville News, Knowable Magazine, and Virginia
Tech news.
\item USAID project mentioned in the USAID Center for Emerging Threats of
Crops Notice of Funding Opportunity as a project that has informed the US
of emerging threats and helped prepare for impending invasion.
\item Supported BII's COVID-19 response efforts in (i)~network construction,
analysis, and validation and (ii)~simulation analytics. 
\item Invited talks in Egypt and Indian Council of Agricultural Research,
India. Talks in various conferences in national and international venues on
invasive species modeling: Ethiopia, India, International Congress of
Entomology (Orlando), Symposium on Integrated Pest Management (Washington
DC).
\item Webinar: New Approaches to Control the South American Tomato Leaf
Miner \emph{Tuta absoluta}, April 2018
\end{enumerate}

\section{\textnormal{\textsc{Mentorship summary}}}
\begin{enumerate}[$\circ$]
    \item Co-advisor for one Masters student (Thesis accepted) (1 paper
    submitted)
    \item Part of thesis committee for three PhD students. I advised on
    several parts of the thesis of two of them.
    \item Research assistants (PhD 1 and Masters students 4)
    \item Undergraduates: 9
    \item High-school: 1
\end{enumerate}

\section{\textnormal{\textsc{Service summary}}}
\begin{enumerate}[$\circ$]
    \item Professional service: 
    \begin{itemize}
        \item Grant review panel (NSF~1, USDA~2, FONDECYT Chile~1)
        \item Senior TPC (IJCAI'21) and TPC (8)
        \item Reviewed papers for a number of journals and conferences
        spanning multiple domains such as Nature comm. Bio., Journal of
        Pest Science, JPDC, ACM Trans. on Algo, Journal of Royal Soc.
        Interface, etc.
    \end{itemize}
    \item Biocomplexity Institute \& Initiative:
    \begin{itemize}
        \item Student and postdoc hiring committee in NSSAC 2018--2020.
        \item Student and postdoc hiring committee in NDSSL 2017--2018.
\item Member of graduate students admission team in NDSSL for the Fall'16
admissions
    \end{itemize}
\end{enumerate}

\section{\textnormal{\textsc{Programmatic contributions}}}
\begin{enumerate}[$\circ$]
\item As PI and Co-PI of the USAID and USDA projects, I have lead the
research in the area of invasive species modeling. This includes
collaborating with people from multiple domains and countries (France,
Senegal, India, Nepal, Bangladesh, and US), presenting in annual meetings,
data exploration, providing content for news reports, mentoring students,
and preparing annual reports. It has resulted in publications in top venues
including Proceedings of the Royal Society Biology, Journal of Pest
Science, Journal of Crop Protection and IEEE BigData conference.
\item COVID-19 response: I led the modeling and development of certain
modules in the synthetic population generation pipeline. This work has
contributed to the generation of US domestic networks as well as global
networks. Also, I developed a network analysis tool set, which is used to
validate our networks and for comparative analysis. These tools have been
applied (i)~to provide weekly inputs to various agencies during certain
periods of the year 2020-21, and (ii)~in manuscripts submitted/under
preparation.
\item DARPA NGS2: I contributed significantly to the theoretical aspects of
this project. Our work on inferring graphical dynamical systems has
resulted in five publications in top AI venues and several workshop
presentations.
\item Fall armyworm in Egypt: In a collaborative effort, I led the modeling
effort to assess the possible spread of Fall armyworm in Egypt. This was
funded by USAID mission in Egypt.
\item Participated in a number of proposal writing efforts every year.
\end{enumerate}

\section{\textnormal{\textsc{Software and Datasets}}}
\begin{enumerate}[$\circ$]
\item Multi-pathway simulator: I have led the development of a simulation
framework to study the multi-pathway spread of invasive species. It
consists of a simulator of a generic network diffusion process implemented
using vectorized methods in Python, a multi-scale temporal network module,
implementation of algorithms for calibration and interventions, modules for
model space exploration using computing clusters, regression tests, and various
visualization tools. Domestic trade networks have been constructed for
several countries using multiple datasets and expert knowledge. The
resulting simulation framework has been applied in multiple studies. The
simulator and synthetic datasets are publicly available and are constantly
updated.
\item High-resolution synthetic population models and datasets: Our group
(NSSAC) has been synthesizing highly-detailed population models from
multiple data sources for more than~15 years. Over the years, these
datasets have been applied in epidemiology (COVID-19, Ebola, influenza,
malaria, etc.), transportation, disaster preparedness, resilience and
sustainability. I have played a prominent part in the Biocomplexity
Institute's COVID-19 response on the modeling and development of the
synthetic population networks. I co-led the design and implementation of
the physical contact network construction module. I applied concepts from
geometric intersection graphs and parallelization to speed up the network
generation. I have also developed a tool for analyzing the generated
networks. It has been regularly applied to compare different networks,
visualize, and validate our models. This software has been well integrated
in to our synthetic population pipeline.
\item Deep learning and remote sensing: We have developed a convolutional
neural network (CNN) framework to predict the distribution of invasive
plants using multispectral satellite images and field survey data.  Our
robust training and evaluation framework employs multiple hold-out approach
for model selection and transfer learning to cope with data challenges
imposed by field survey and imagery constraints.  Multi-spectral
remote-sensed images from multiple satellites were used in this study. We
have developed the framework for optical calibration, sharpening, and
interpolation of the images towards feature vector extraction. Popular
deep neural networks had to be adapted for satellite images. Transfer
learning approaches were applied. The framework is applied to study the
distribution of multiple invasive plants in the Chitwan-Annapurna Landscape
of Nepal, a biodiversity hotspot.
\end{enumerate}

\section{\textnormal{\textsc{Transdisciplinary team science}}}
My work involves leading and being part of large teams of researchers from
different fields.  As PI of two USAID and USDA projects, I have led BII’s
research in the area of invasive species modeling. As PI, I have initiated
multiple projects collaborating with researchers from several countries
(US, France, Senegal, India, Nepal, and Bangladesh). Example projects
include (i)~modeling the spread of a pest of the tomato plant, \tutafull{} in
Southeast Asia and West Africa involving entomologists, economists,
modelers and computer scientists and (ii)~mapping invasive plants in Nepal
using remote-sensing and machine learning involving botanists and
geoinformation specialists. I play a major role is several large team projects in the
Biocomplexity Institute as well. These include studies related to
computational epidemiology such as COVID-19 response, disaster
preparedness, and computational social science.

\section{\textnormal{\textsc{Selected recent publications}}}
\nobibliography*
\begin{enumerate}[$\circ$]
\item \bibentry{hoops2021wsc}
\item \bibentry{adiga2020booleangames}
\item \bibentry{adiga2020bounds}
\item \bibentry{mcnitt2019assessing}
\item \bibentry{venkatramanan2020modeling}
\item \bibentry{adiga2019pac}
\item \bibentry{adiga2018learning}
\item \bibentry{campos2017western}
\item \bibentry{adiga2017inferring}
\end{enumerate}


\clearpage


\end{resume}

\clearpage
\moveleft1.0\hoffset\centerline{\large\bf Details\hfill} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\begin{resume}
%%%%
\section{\textnormal{\textsc{Education}}}
\textbf{PhD:} \hfill August 2006 -- March 2011\\
Dept. of Computer Science and Automation\\
Indian Institute of Science, Bangalore, India\\ 
%% Adviser: {Dr. L Sunil Chandran}\\
%% {Thesis}: On Dimensional Parameters of Graphs and Posets\\
~\\
\noindent\textbf{Master of Science (Engg):} \hfill August 2001 -- August 2003\\
Dept. of Electrical Engineering,\\
Indian Institute of Science, Bangalore, India\\
%% Adviser: Dr. K R Ramakrishnan\\
%% {Thesis:} Cyclic Multirate Structures Based on Symmetric-Periodic
%% Sequences\\
~\\
\noindent\textbf{Bachelor of Engineering:} \hfill 1996 -- 2000\\
Bangalore University (B.M.S. College of Engineering)\\
Telecommunication Engineering
%%%%%%
\section{\textnormal{\textsc{Work\,\,\,\, Experience}}} 
{Research Assistant Professor} \hfill Jul 2016 -- Oct 2018\\
Senior Research Associate \hfill May 2014 -- Jul 2016\\
Postdoctoral Associate \hfill October 2011 -- May 2014\\
Network Dynamics and Simulation Science Laboratory\\
Biocomplexity Institute of Virginia Tech\\
~~~\\
Research Associate \hfill March 2011 -- September 2011\\
Dept. of Computer Science and Automation, IISc \\
~~~\\
{Beceem Communications Pvt Ltd}\hfill August 2004 -- July 2006\\
Algorithm design for WiMax (802.16) \\
~~~\\
Project Associate \hfill October 2003 -- April 2004\\ 
Project Associate\hfill October 2000 -- August 2001\\ 
Dept. of Electrical Engineering, IISc \\
%% Worked under Dr. P S Sastry on temporal data-mining \\
%% Worked under Dr. K R Ramakrishnan on source \& channel coding and Advanced
%% Encryption Standard (Rijndael)
%%%%%%
\section{\textnormal{\textsc{Grants}}}
\begin{enumerate}[$\circ$]
\item USDA NIFA Foundational and Applied Science Program: \emph{Network
Models of Food Systems and their Application to Invasive Species Spread} \\
Amount:~\$400,000; Duration: Sep'19--Aug'23\\
Role: PI
\item USAID IPM Innovation Labs: \emph{Assessment of Invasive Alien Species Distribution in the Chitwan-Annapurna-Landscape (CHAL) Region, Nepal}\\
Amount:~\$150,000; Duration: Jan'19--Nov'21\\
Role: Co-PI
\item USAID Egypt Mission: \emph{Pest Risk Assessment of the Fall Armyworm,
Spodoptera frugiperda in Egypt}\\ Amount:~\$18,000; Duration:
Oct'17--Dec'17\\ Role: Co PI
%\item
%\noindent\textbf{Pending}\\
\item USAID IPM Innovation Labs: \emph{A High-resolution Interaction Based
Approach to Modeling the Spread of Agricultural Invasive Species}\\
Amount:~\$1,000,000 (\$800,000 for Virginia Tech); Duration: Oct'15--Nov'21\\
Role: PI
\end{enumerate}
\clearpage

\noindent
\textbf{Current efforts/pending:}\\
\begin{enumerate}[$\circ$]
\item USAID Feed the Future Innovation Lab for Current and Emerging Threats
to Crops Catalog of Federal Domestic Assistance, 2021.
\item NSF HDR Institute: Data Science for Transportation, Epidemiology and
Power (DataSTEP), 2021 (submitted).
\item NSF AI Institute: Agricultural AI for Transforming
Workforce and Decision Support (AgAID), 2021.
\end{enumerate}
%%%%%%%%%%%%
\section{\textnormal{\textsc{Awards}}}
\begin{enumerate}[$\circ$]
   \item ``DSFEW Early Career Researchers Travel Fund'', KDD 2016.
\item ``Honorable Mention For Outstanding Novelty of Research
Question'' award for the paper ``Sensitivity of Diffusion Dynamics to
Network Uncertainty'' in AAAI'13.
\item Infosys Fellow: awarded to select
PhD candidates in IISc by Infosys Technologies Ltd. 
\item Secured All India Rank of 34 in GATE 2000 (EC), a national level
entrance exam for post graduate studies.
\item Ranked 7th in Bangalore University in Telecommunication Engg. (Year 2000).
\end{enumerate}
%%
%%
\section{\textnormal{\textsc{News}}}
\begin{enumerate}[$\circ$]
\item 
\href{https://knowablemagazine.org/article/technology/2020/virtual-agents-change-how-computers-are-mapping-covid19s-future}{Virtual
agents of change: How computers are mapping Covid-19’s future}, Knowable
Magazine, 2020.
\item
\href{https://www.agrilinks.org/post/q-why-mapping-spread-invasive-species-above-so-important-prevention-efforts-below}{Agrilinks
article on USAID Invasive Species project; 2020.}
\item
\href{https://www.cbs19news.com/story/41855331/grant-to-help-model-potential-arrival-of-invasive-species-and-protect-tomato-crops?utm_source=cmpgn_news&utm_medium=email&utm_campaign=vtUnirelNewsDailyCMP_031320-f%2Fs}{Charlottesville
News (CBS19) announcing the USDA FACT project; 2019.}
\item
\href{https://vtnews.vt.edu/articles/2018/03/outreach-ipmegyptfaw.html}{Virginia
Tech provides key intel in U.S. and Egyptian-led battle against a major
pest; 2018}
\item
\href{https://vtnews.vt.edu/articles/2018/02/outreach-ipmnexus.html}{Countries
get heads up about leafminer invasion thanks to Virginia Tech} (also picked
up by Wisconsin Farmer and Agrilinks)
\item
\href{https://vtnews.vt.edu/articles/2016/05/outreach-oiredinnovationlabawards.html}{Virginia Tech awards more than \$11 million to help feed people in
developing countries}
\item
\href{https://www.bi.vt.edu/ndssl/news/virginia-tech-research-team-fights-the-spread-of-invasive-pests}{Virginia
Tech Research Team Fights the Spread of Invasive Pests}
\end{enumerate}
%%
\section{\textnormal{\textsc{Selected Talks}}} 
\begin{enumerate}[1.]
    \item Boolean Games: Inferring Agents' Goals Using Taxation Queries,
    International Joint Conference on Artificial Intelligence (IJCAI'20)
    (virtual), January 2021.
    \item A Deep Learning Framework for Invasive Species Mapping using
    High-Resolution Satellite Imagery, ASPRS 2020 Annual Conference (virtual), June 2020.
    \item (\textbf{Invited}) Network Dynamical Systems: Theory and
    Applications, Indian Institute of Technology, Hyderabad, India,
    November 2019.
    \item Modern AI Techniques to Understand the Spatio-temporal Spread of
    Invasive Alien Plants: Approaches and Challenges, International Plant
    Protection Congress, Hyderabad, India, November 2019.
    \item Modeling the multi-pathway spread of agricultural pests using
    network science, International Plant Protection Congress, Hyderabad,
    India, November 2019.
    \item Understanding the Role of Seasonal Food Trade Networks in Invasive
Species Spread, SIAM Network Science, Snowbird, Utah,
    May 2019.
    \item (\textbf{Invited}) How to stop an epidemic? Networked dynamical
    systems, games and near-optimal algorithms, Indian Institute of
    Technology, Dharwad, October 2018.
    \item (\textbf{Invited}) Multi-pathway models to assess the threat of
    invasive species spread, Indian Agricultural Research Institute, Delhi,
    October 2018.
    \item Multi-pathway models to understand the spread and impact of
    \emph{Tuta
    absoluta}, International Conference on Biological Control (ICBC),
    September 2018.
    \item (\textbf{Webinar}) New Approaches to Control the South American Tomato
   Leaf Miner \emph{Tuta absoluta}, April 2018
   \item Monitoring the spread of {\it Tuta absoluta} using a
    multi-layered network based modeling framework, \emph{9th International
    IPM Symposium}, Baltimore, March 2018
    \item (\textbf{Invited}) Modeling the Spread of Fall Armyworm,
    \emph{Fall Armyworm Workshop}, Adis Ababa, 2017
    \item (\textbf{Invited}) Understanding the role of human-mediated
    pathways in pest spread: Case study of \emph{Tuta absoluta}, \emph{12th
    Arab Congress of Plant Protection}, Hurghada, 2017
   \item Monitoring spread of T. absoluta using a multi-layered network
   based modeling framework, \emph{Symposium on Global Spread and Management
   of the South American Tomato Leafminer, Tuta absoluta. International
Congress of Entomology}, Orlando, 2016
\item (\textbf{Invited}) How to stop an epidemic?  Games and near-optimal
algorithms, \emph{Dept. of Computer Science and Automation, Indian
Institute of Science}, Bangalore, 2014
\item (\textbf{Invited}) Sensitivity of Dynamical Properties to Network
Uncertainty, \emph{Dept. of Computer Science and Automation, Indian
Institute of Science}, Bangalore, 2013
\end{enumerate}
%%
\iftoggle{compact}{
\section{\textnormal{\textsc{Selected publications}}} 
}{
\section{\textnormal{\textsc{Publications}}} 
}
\noindent\textbf{Journal articles}\\
\begin{enumerate}[1.]%%[$\circ$]
    \item \bibentry{cedeno2020networked}
    \item \bibentry{poudel2020predicting}
\item \bibentry{de2021thermal}
\item \bibentry{mcnitt2019assessing}
\item \bibentry{maharjan2019predicting}
\item \bibentry{venkatramanan2020modeling}
\iftoggle{compact}{}{
\item \bibentry{adiga2019graphical}
}
\item \bibentry{adiga2018disparities}
\iftoggle{compact}{}{
\item \bibentry{adiga2018sublinear}
}
\item \bibentry{campos2017western}
\iftoggle{compact}{}{
\item \bibentry{adiga2017inferring}
\item \bibentry{adiga2017activity}
}
\item \bibentry{zhang2016near}
\item \bibentry{adiga2014sensitivity}
\item \bibentry{adiga2014representing}
\iftoggle{compact}{}{
\item \bibentry{adiga2014constant}
\item \bibentry{wu2014limit}
}
\item \bibentry{adiga2014lower}
\iftoggle{compact}{}{
\item \bibentry{adiga2014cubicity}
}
\item \bibentry{adiga2011boxicity}
\item \bibentry{adiga2010hardness}
\item \bibentry{adiga2010cubicity}
\item \bibentry{adiga2009cubicityThreshold}
\end{enumerate}
\clearpage
\noindent\textbf{Refereed conference proceedings}\\
\begin{enumerate}[1.]%%[$\circ$]
\item \bibentry{hoops2021wsc}
\item \bibentry{adiga2020booleangames}
\item \bibentry{adiga2020bounds}
\item \bibentry{adiga2019validating}
\item \bibentry{hu2019modeling}
\item \bibentry{adiga2019pac}
\iftoggle{compact}{}{
\item \bibentry{cedeno2019mechanistic}
\item \bibentry{ren2018generative}
}
\item \bibentry{adiga2018inferringprob}
\item \bibentry{adiga2018learning}
\iftoggle{compact}{}{
\item \bibentry{adiga2017kserver}
\item \bibentry{venkat2017towards}
}
\item \bibentry{adiga2016delay}
\item \bibentry{adiga2016temporal}
\iftoggle{compact}{}{
\item \bibentry{adiga2015csd}
}
\item \bibentry{zhang2015group}
\iftoggle{compact}{}{
\item \bibentry{adiga2015inferring}
\item \bibentry{adiga2015network}
\item \bibentry{adiga2015effect}
}
\item \bibentry{saha2015spectrum}
\item \bibentry{saha2014game}
\iftoggle{compact}{}{
\item \bibentry{adiga2013modelingurban}
}
\item \bibentry{adiga2013subgraph}
\item \bibentry{adiga2013robust}
\item \bibentry{adiga2013sensitivity}
\item \bibentry{adiga2012representing}
\iftoggle{compact}{}{
\item \bibentry{adiga2012polynomial}
\item \bibentry{adiga2011cubicity}
\item \bibentry{adiga2011constant}
\item \bibentry{adiga2010parameterized}
\item \bibentry{adiga2010boxicity}
\item \bibentry{adiga2009cubicity}
\item \bibentry{adiga2003design}
}
\end{enumerate}
\iftoggle{compact}{}{
\noindent\textbf{Workshop/Extended abstract}\\
\begin{enumerate}[1.]
\item \bibentry{adiga2020boolean}
\item \bibentry{fox2019learning}
\item \bibentry{adiga2019inferring}
\item \bibentry{adiga2019understanding}
\item \bibentry{nath2018using}
\item \bibentry{adiga2018using}
\item \bibentry{adiga2018inferring}
\item \bibentry{geneiusWu}
\item \bibentry{hybridModelsVenkat}
\item \bibentry{climexSridhar}
\item \bibentry{venkat2016kdd}
\item \bibentry{adiga2015bme}
\item \bibentry{adiga2015synthetic}
\item \bibentry{adiga2012route}
\end{enumerate}
\noindent\textbf{Reports}\\
\begin{enumerate}[1.]
\item \bibentry{heinrichs2018pest}
\end{enumerate}
}
%% \noindent\textbf{Under review/Technical reports}\\
%% \begin{enumerate}[1.]
%% \item \bibentry{mortveit2015synthetic}
%% \item \bibentry{adiga2015sublinear}
%% \item \bibentry{adiga2015interaction}
%% \end{enumerate}
%%
\section{\textnormal{\textsc{Students \\Current/Past}}}
\noindent\textbf{Student thesis/project committee}\\
Manisha Sudhir (Spring'20--Spring'21) (Co-adviser with Anil
Vullikanti)\\
Prathyush Sambaturu (PhD, UVA) \\
Tanay Mehta (PhD, Northeastern University) \\
Sudip Saha (PhD, Virginia Tech)\vspace{.2cm}\\
\noindent\textbf{PhD} (GRA)\\
Sichao Wu (Thesis adviser: Henning Mortveit)\vspace{.2cm}\\
\noindent\textbf{Masters} (GRA)\\
Sanchit Sinha (Spring'21)\\
Aniruddha Dave (Fall'20)\\
Daniel Perez Lazarte (Fall'19, Spring'20)\\
Joseph McNitt (Thesis adviser: Henning Mortveit)\vspace{.2cm}\\
\noindent\textbf{Undergraduates}\\
Neha Pattanaik (Summer'21),
Penina Waghalter (Summer'21),
Nicholas Palmer (Summer'21),
Johnny Yang (Fall'20, Spring'21),
Surbhi Singh (Fall'19--Spring'20),
Ethan Choo (Summer'19),
Katie Liu (Summer'19),
Bryan Kaperick (Spring'16--Spring'17), and
Amleshwar Kumar (Intern: Fall'16) \vspace{.2cm}\\
\noindent\textbf{High school}\\
Manu Amundsen (Spring'21)
%%\section{\textnormal{Memberships}}
%%\begin{enumerate}[$\circ$]
%%\item IEEE member
%%\end{enumerate}
%%
%%
\section{\textnormal{\textsc{Professional Service}}}
\noindent\textbf{Guest editor}\\
Journal of Indian Institute of Science (2021)\smallskip\\
\noindent\textbf{Senior Technical Program Committee member}\\ 
IJCAI~(2021)\\
\noindent\textbf{Technical Program Committee member}\\ 
ANNSIM~(2021), AIKE~(2018--2021), PhD-ASONAM (2020), INFOCOM~(2019), CSoNet~(2016), CONECCT~(2015), SDM-Networks~(2015), SIAMNS~(2015)\smallskip\\
\noindent\textbf{Grant Review}\\
USDA~(Spring'20 and Fall'20) (Grant review panelist)\\
NSF~(2018) (Grant review panelist)\\
National Fund for Scientific and Technological Development (FONDECYT),
Chile\smallskip\\
\noindent\textbf{Reviewer}\\ 
\noindent
Biological Control (2021),
Nature Comm. Biology (2021),
Applied Network Science (2021, 2020, 2019),
Journal of Pest Science~(2020, 2018), 
International Journal of epidemiology~(2019),
Pest Management Science~(2019), 
Journal of Parallel and Distributed Computing~(2019), 
Australasian Journal of Combinatorics~(2018, 2015),
FPSAC~(2017),
ACM Transactions on Algorithms~(2017),
Journal of Royal Society Interface~(2017), INFOCOM~(2016, 2015), Order~(2015), 
Algorithmica~(2014), Journal of Autonomous Agents and Multi-Agent
Systems~(2013), 
Information Processing Letters~(2012), 
Graphs and
Combinatorics~(2011), CATS~(2011)\bigskip\\
\iftoggle{compact}{}{
\noindent\textbf{Miscellaneous}\\ 
\begin{enumerate}[$\circ$]
\item Student and postdoc hiring committee in NSSAC 2018-present
\item Student and postdoc hiring committee in NDSSL 2017-2018
\item Member of graduate students admission team in NDSSL for the Fall'16
admissions
\item Organized NDSSL graduate seminar series for the academic year 2013-2014
\end{enumerate}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For visa
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iftoggle{visa}{
\newpage
\section{\textnormal{PhD \textsc{Committees}}}
Prathyush Sambaturu (Univ. of Virginia) \\
Tanay Mehta (Northeastern University) \\
Sudip Saha (Virginia Tech)
\section{\large{Job description}:}
\vspace{.8cm}
%%
\section{\textnormal{{Current job}}}\label{sec:currentJob}
My work is in the areas of network science, algorithms, combinatorics and
game theory. My research focus is on the design and analysis of
computational models and their application to solve real-world problems.
Through interdisciplinary collaborative efforts, I (i)~contribute to the
understanding of structural and dynamical properties of networks,
(ii)~develop efficient and practical algorithms for various optimization
problems, and (iii)~take part in the design and implementation of complex
simulation systems. Some of the application areas of my work include
invasive pest modeling, computational epidemiology, transportation and
social sciences.
%%
\section{\textnormal{{Senior Research Associate}}}\label{sec:sra}
(May 2014 -- Jul 2016) Job description is same as current
job.\smallskip
%%
\section{\textnormal{{Postdoctoral associate}}}\label{sec:postdoc}
(October 2011 -- May 2014) Job description is same as current
job.\smallskip
%%
\section{\textnormal{{Research associate}}}
(March 2011 to October 2011) I continued my PhD work.\smallskip
%%
\section{\textnormal{PhD}}
(August 2006 to March 2011)
The work of this thesis falls into the broad area of theoretical computer
science, and in particular, concerns graph theory, combinatorics and
algorithms. We study some geometric representations of graphs and
dimensional properties of graphs and posets. The main objective is
to represent a graph using certain geometric objects. Many problems
on graphs which are otherwise computationally hard to solve can be
solved efficiently if the graph in consideration has a simple geometric
representation. In the parlance of theoretical computer science, many
NP-hard problems may be either solved in polynomial time or at least
have good approximation algorithms when a graph has a low dimensional
geometric representation. Besides, the representations which we consider
have applications in various other scientific disciplines: ecology,
social sciences, psychology, telecommunication and operations research.
Our contribution to this area are as follows:
(1)~We have developed efficient algorithms to
obtain such representations for certain specific classes of graphs.
(2)~We have complexity results which show that for some classes of graphs, it
is computationally hard to obtain such a representation.
(3)~We give a general framework relating different representations.
%%
\section{\textnormal{Beceem Communications}}\label{sec:beceem}
(August 2004 -- July 2006)
I was part of the algorithm development and simulation group. My
work involved the design and implementation of algorithms for WiMax
(802.16), a wireless broadband standard. I worked on (1)~implementing
and maintaining the error control coding module in the simulator, 
%I had
%to implement the turbo encoder and decoder, a class of high-performance
%forward error correction (FEC) codes. The language in which the simulator
%was implemented was MATLAB.
(2)~The creation of an interface between
the simulator (coded in MATLAB) and the chip (coded using Verilog), 
%I was involved in this project right from its initiation. This interface
%provided the vital link between the two modules and enabled the
%verification.
(3)~Running simulations by
varying parameters such as type of codec, channel, etc.
%%
\section{\textnormal{Project associate}}\label{sec:dataMining}
(October 2003 to April 2004)
The work was in the area of temporal data-mining. 
%We were given access
%to months of data from a manufacturing line of a factory. Each time
%the manufacturing process stopped, the time and the reason behind
%the stoppage was logged into the system. The reasons could be anything
%ranging from the mundane (like a lunch break!) to the very technical ones.
%Each possible reason for stoppage was represented by a symbol. Hence,
%the data given to us was in the form of very long sequences of symbols
%with time stamp. 
The aim was to extract interesting patterns from a sequence of logs
obtained from a manufacturing process by using machine learning techniques.
%The main question
%that our tool had to answer was: Does a particular sequence of breakdowns
%in one section of the manufacturing line influence a breakdown in some
%other section?
%My work was mainly implementation oriented and could be divided into two
%parts.  Firstly, 
I helped in the development of the data mining tools for this purpose.
%to filter the data 
%(like
%for example, removing the symbols corresponding to lunch break). This
%required using some scripting languages. Secondly, 
%I had to assist in
%enhancing our data mining tool by implementing new search techniques. The
%language of implementation was C.
%
%I was also involved in administrative activities related to the project and
%conducting exams.
%%
\section{\textnormal{MSc}}\label{sec:mastersAbstract}
(August 2001 to September 2003)
We proposed a framework for implementing wavelet transforms in the
frequency domain particularly for application on images and analyzed the
performance of our methods in the context of image compression by comparing
our methods with the methods used in JPEG and JPEG 2000 image compression
standards.
%%
\section{\textnormal{Project associate}}\label{sec:turbo}
(October 2000 -- August 2001)
I worked in the area of communication theory. My work involved studying
the area of joint source and channel coding and other areas related to
telecommunication. I implemented some algorithms like turbo codecs and
Rijndael in MATLAB and helped in administrative activities.

\newpage
\section{Personnel Manager Information}
\noindent{\bf Madhav V. Marathe}

\noindent Director, Network Dynamics and Simulation Science Laboratory
and Professor, Computer Science\\
\\
\noindent{\bf Mailing Address:} \\
\noindent Network Dynamics and Simulation Science Laboratory \\
\noindent Virginia Bioinformatics Institute \\
\noindent Virginia Polytechnic Institute and State University \\
\noindent Research Building XV (0477) \\
\noindent 1880 Pratt Drive \\
\noindent Blacksburg, VA 24061 \\
\noindent USA \\
\\
{\bf Tel:} 540-231-8252\\
{\bf Fax:} 540-231-2891\\
{\bf Email:} marathe@vt.edu\\
{\bf Web page:}
http://www.vbi.vt.edu/ndssl/people/people-profile/Madhav-Marathe \\
\\
\\
\noindent{\bf L. Sunil Chandran}\\
Associate Professor,
Department of Computer Science and Automation
Indian Institute of Science\\
\\
\noindent{\bf Mailing Address:} \\
CSA Department\\
Indian Institute of Science\\
Bangalore - 560012\\
\\
{\bf Tel:} +91-80-22932368\\
{\bf Fax:} +91-80-23602911 \\
{\bf Email:} sunil@csa.iisc.ernet.in\\
{\bf Web page:} http://drona.csa.iisc.ernet.in/\textasciitilde sunil/


   }{}
\end{resume}
\bibliographystyle{abbrv}
\nobibliography{refs}
\end{document}
